---
title: "24203206 Homework -1"
author: "Jonas Robin Nadar|24203206"
format: pdf
editor: visual
execute:
  warning: false  
  error: false    
  message: false
  echo: false
---

```{r}
#Loading Libraries
library(ggplot2)
```

## Introduction {#sec-introduction style="color: purple"}

The \`sleep\` dataset in R shows the effect of two soporific drugs *(increase in hours of sleep compared to control)* on 10 patients.

## Dataset Overview {#sec-dataset-overview style="color: purple"}

The dataset has 20 rows and 3 columns

| Column Name | Type    | Description                |
|-------------|---------|----------------------------|
| extra       | numeric | increase in hours of sleep |
| group       | factor  | drug given                 |
| ID          | factor  | patient ID                 |

**NOTE:** The `group` variable name may be misleading about the data: [*They represent measurements on 10 persons, not in groups.*]{.underline}

```{r}
#Loading the Data
data(sleep)
str(sleep)
```

## Plot

From @fig-box we can see that group 2 medicine is performing better than group 1 as on average the increase in sleep is more in group 2

```{r}
#| label: fig-box
#| fig-cap: "Box plot of increase in sleep duration across different drug groups"
#| fig-width: 8
#| fig-height: 5
ggplot(sleep, aes(x = group, y = extra, fill = group)) + geom_boxplot() + labs(title = "Increase in Sleep Duration by Drug Group", x = "Drug Group", y = "Increase in Sleep (Hours)") + theme_minimal()
```

### Summary

The box plot shows that the second drug generally leads to a greater increase in sleep duration. Although there's overlap, the median and overall distribution suggest better efficacy from drug group 2.
